A note on multi agent learning

### 2016-06-27 multiAgentLearning/paper/article.tex
todos out of the comments

\abstract{
  %TODO abstract
  \todo[inline]{abstract missing}
}
\section{Introduction}
\toReview
Satisficing play was originally introduced
to try and limit the computation power that earlier models required of human
behavior \citep{herbert}. Originating from the field of economics, they
wanted to use a model that was not ``super intelligent''.

@@

The Nash equilibrium of this games lies on Defect,Defect. However, all but
that action are pareto optimal actions. So the Nash equilibrium would be the
``right'' strategy to play if the game is only played once, but if you repeat
the game against the same opponent, interestingly enough you can ``solve''
the prisoners dilemma by ``teaching'' the opponent to cooperate.

@@

\section{Satisficing compared to other learning methods}
\drafting
With help of the work of \citep{crandall} saticificing play is compared
to Q-learning and WOLF-PHC.
Q-learning is explained briefly with help of \citep{sandholm} and WOLF-PHC
with help of \citep{bowling}.

@@

\bibliography{main}

>>>>

\abstract{
  %TODO abstract
  \todo[inline]{abstract missing}
}
\todo{be more critical? maybe it depends to much on its paremeters?
  Or which game types are good for saticifing play?
}
\todo{misses callouts, intermezzi and quotes}
\section{Introduction}
\toReview
Satisficing play was originally introduced
to try and limit the computation power that earlier models required of human
behavior \citep{herbert}. Originating from the field of economics, they
wanted to use a model that was not ``super intelligent''.

@@

The Nash equilibrium of this game lies on Defect,Defect. However, all but
that action are pareto optimal actions. So the Nash equilibrium would be the
``right'' strategy to play if the game is only played once, but if you repeat
the game against the same opponent, interestingly enough you can ``solve''
the prisoners dilemma by ``teaching'' the opponent to cooperate.

@@

\section{Satisficing compared to other learning methods}
\drafting

With help of the work of \citep{crandall} saticificing play is compared
to Q-learning and WOLF-PHC.
Q-learning is explained briefly with help of \citep{sandholm} and WOLF-PHC
with help of \citep{bowling}.

@@

\todo{check }
\bibliography{main}
